Compiler and Runtime Support for Functions-as-a-Service (FaaS)

### 2021-12-09 paper/paper.tex
[paper]: add implementation

\section{Implementation}

>>>>

\section{Implementation}
The prototype compiler was built using LLVM 13.0.0. Both prototype runtimes (profiler and allocator) 
were implemented using \texttt{C++}. Profiler-guided compiler instrumentation for the custom 
allocator was not fully implemented and tested in this prototype due to its engineering effort.

In the allocator runtime in particular, bump allocators are organized in a red-black tree (\texttt{std::map})
where the key is the block size. Each bump allocator object allocates from an initial pool
containing (a default) 32 entries (each entry is sized to the block size). If there are no free entries
in the pool, another pool is allocated. Pools for a bump allocatore are also stored in a 
red-black tree (\texttt{std::map}), mostly to aid \DALLS .

Initialization for the compiler-directed memory pool and bump allocators with known block size at 
compile-time are injected by the compiler into a runtime function marked with the attribute 
\texttt{constructor}. Although initialization is theoretically most performant when done in parallel
to FaaS startup, this was not implemented in the system prototype.

Finally, all workloads are implemented in \texttt{C} and only use \textit{libc} \texttt{malloc} and 
\texttt{free}. Although most FaaS workloads are implemented in higher-level languages, the 
simplicity of the dynamic memory interface makes it very simple for the prototype compiler and 
runtime to target, as all \ALLS\ and \DALLS\ are obviously explicit. Targeting higher-level 
languages remains a future work.
